Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-14 write-ups/PLDI/paper.tex
Edit overhead

\begin{table}
\small
\centering
\begin{tabular}{ l c c c }
Chip & HD520 & HD5500 & IRIS\\
\hline
overall gm  & $1.20$ & $1.15$ & $1.08$ \\
overall max & $1.75^{\ast}$ & $1.45^{\dagger}$ & $1.37^{\ddagger}$ \\

\hline
barrier gm & $1.18$ & $1.16$ & $1.07$ \\
barrier max & $1.75^{\ast}$ & $1.45^{\dagger}$ & $1.37^{\ddagger}$ \\

\hline
wk.steal. gm & $1.42$ & $1.10$ & $1.12$ \\
wk.steal. max & $1.42^{\diamond}$ & $1.18^{\diamond}$ & $1.23^{\diamond}$ \\

@@

\paragraph{Experimental setup}
\ADComment{Describe the data we are gathering.}
The introduction of cooperative scheduling primitives introduces an
overhead even if no killing, forking or resizing ever happen. We
measure this overhead by comparing execution times of the original
kernel and the cooperative one, forcing the scheduler to never modify
the number of active workgroups. Since the cooperative kernel contains
the non-persistent task code anyway, its occupancy bound may be less
than the original kernel; we make sure to use this occupancy bound as
the number of workgroups for the original kernel in order to compare
relevant execution times.

\HEComment{Also include this occupancy reduction as an overhead?}

>>>>

\begin{table}
\small
\centering
\begin{tabular}{ l l l l }
Chip & HD520 & HD5500 & Iris\\
\hline
overall geo. mean  & $1.20$ & $1.15$ & $1.08$ \\
overall max & $1.75^{\ast}$ & $1.45^{\dagger}$ & $1.37^{\ddagger}$ \\

\hline
barrier geo. mean & $1.18$ & $1.16$ & $1.07$ \\
barrier max & $1.75^{\ast}$ & $1.45^{\dagger}$ & $1.37^{\ddagger}$ \\

\hline
wk.steal. geo. mean & $1.42$ & $1.10$ & $1.12$ \\
wk.steal. max & $1.42^{\diamond}$ & $1.18^{\diamond}$ & $1.23^{\diamond}$ \\

@@

Cooperative scheduling primitives entails an overhead even if no
killing, forking or resizing ever happen. We measure this overhead via
the execution time ratio between the original kernel and the
cooperative one, forcing the scheduler to never modify the number of
active workgroups. Since the cooperative kernel contains the
non-persistent task code anyway, its occupancy bound may be less than
the original kernel; we make sure to use this occupancy bound as the
number of workgroups for the original kernel in order to compare
relevant execution times. \HEComment{Do we need to mention the
  possible occupancy reduction as an overhead?}

\paragraph{Results} \ADComment{Discuss the results.}
\mytab~\ref{tab:overhead} lists overhead slowdown ratios, both
geometric mean and maximum value. The overhead is below a 2 times
slowdown even in the worst case. We consider these results as
acceptable, given that our SVM-based scheduler performance is likely a
far upper bound of what a scheduler implemented directly in the
runtime could offer.
